The Privacy of Private Browsing

### 2013-12-11 finalproject/paper.tex
added table, need to fix apostrophes

\documentclass[pdftex,letterpaper,titlepage,11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}

@@

  \section{Introduction}
  Most modern web browsers offer some sort of private browsing mode. This is
  supposed to allow users to view web content without other users of the same
  computer being able to determine what websites were visited. What is kept
  private and what is not differs from browser to browser. An overview of the
  most common browsers for Windows and Linux is provided below.

@@

  \begin{thebibliography}{9}
    \bibitem{verdi13}
      Verdi, Michael et al. ``Private Browsing.'' \emph{Mozilla Support}. 
      Mozilla Foundation, 29 Mar. 2013. Web. 10 Dec. 2013. 
      $<$\url{https://support.mozilla.org/en-US/kb/private-browsing-browse-web-
      without-saving-info}$>$.
    \bibitem{google13}
      ``Chrome Browser.'' \emph{Chrome}. Google, 18 Nov. 2013. Web. 10 Dec. 
      2013. $<$\url{https://www.google.com/intl/en/chrome/browser/
      features.html#privacy}$>$.
    \bibitem{ie13}
      ``InPrivate Browsing.'' \emph{Microsoft Windows}. Microsoft, 10 Dec. 
      2013. Web. 10 Dec. 2013. $<$\url{http://windows.microsoft.com/en-us/
      internet-explorer/products/ie-9/features/in-private}$>$.

>>>>

\documentclass[pdftex,letterpaper,titlepage,11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{array}

@@

  \section{Introduction}
    \subsection{Browser Overview}
    The following table summarizes the web browsers that will be considered in
    this paper. The features that a particular web browser's private mode is
    believed to have comes from the developers of the browser. Note that all
    browsers run on both Windows and Linux, with the exception of Internet
    Explorer, which runs only on Windows.\cite{verdi13}\cite{google13}
    \cite{ie13}

    \begin{center}
      \begin{tabular}{|m{'5cm'}|c|c|c|}
        \hline
        Property & Mozilla Firefox & Google Chrome & Internet Explorer \\
        \hline
        Browser history & X & X & X \\
        \hline
        Form data & X &  & X \\
        \hline
        Search bar data & X &  & X \\
        \hline
        Passwords & X &  & X \\
        \hline
        Downloads & X & X &  \\
        \hline
        Cookies & X & X & X \\
        \hline
        Cached files & X &  & X \\
        \hline
        Simulataneous sessions with different privacy settings & X & X & X \\
        \hline
        Hides activity from ISP &  &  &  \\
        \hline
        Hides activity from websites &  &  &  \\
        \hline
      \end{tabular}
    \end{center}

  This paper also discusses the Tor browser. Unlike Firefox, Chrome, and
  Internet Explorer, the Tor browser connects users to the internet using the
  Tor network. This does much more to preserve browsing anonymity than the
  browsers listed above. TODO finish this\ldots lazy.

  Most modern web browsers offer some sort of private browsing mode. This is
  supposed to allow users to view web content without other users of the same
  computer being able to determine what websites were visited. What is kept
  private and what is not differs from browser to browser. An overview of the
  most common browsers for Windows and Linux is provided below.

@@

  \begin{thebibliography}{9}
    \bibitem{verdi13}
      Verdi, Michael et al. ``Private Browsing.'' \emph{Mozilla Support}. 
      Mozilla Foundation, 29 Mar. 2013. Web. 10 Dec. 2013. 
      $<$\url{http://support.mozilla.org/en-US/kb/private-browsing-browse-web-
      without-saving-info}$>$.
    \bibitem{google13}
      ``Chrome Browser.'' \emph{Chrome}. Google, 18 Nov. 2013. Web. 10 Dec. 
      2013. $<$\url{http://www.google.com/intl/en/chrome/browser/
      features.html#privacy}$>$.
    \bibitem{ie13}
      ``InPrivate Browsing.'' \emph{Microsoft Windows}. Microsoft, 10 Dec. 
      2013. Web. 10 Dec. 2013. $<$\url{http://windows.microsoft.com/en-us/
      internet-explorer/products/ie-9/features/in-private}$>$.
    \bibitem{tor13}
      ``Tor Project: Overview.'' \emph{Tor}. Tor, 7 Dec. 2013. Web. 10 Dec. 
      2013. $<$\url{http://www.torproject.org/about/overview.html.en}$>$.
